A review on Generative Learning in Computer Vision

### 2020-05-02 paper.tex
renamed files
added intro

\begin{abstract}
This document is a model and instructions for \LaTeX.
This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
or Math in Paper Title or Abstract.
\end{abstract}

@@

\section{Introduction}
This document is a model and instructions for \LaTeX.
Please observe the conference page limits.

>>>>

\begin{abstract}

\end{abstract}

@@

\section{Introduction}
Artificial intelligence has made it possible for computers to learn from experiences and perform simple tasks which a human can easily do. Visual perception by human-like object recognizing abilities is once such task which scientists have been able to teach computers. The field of teaching computers to percieve its environment is called as computer vision.

In the past few years due to advancement and innovation in computing power especially unlocking GPU based distributed computing, computer scientists have achieved good success in able to teach computers to do complex tasks beyond classification like object detection, image segmentation, and object tracking.
